%-------------------------
% Resume in Latex
% License : MIT
% Edited: Prem Shah (Author: Sourabh Bajaj)
%------------------------

\documentclass[letterpaper,11pt]{article}
%\renewcommand{\familydefault}{\sfdefault}
%\fontfamily{garamond}
\usepackage{times}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemTwo}[1]{
	\item\small{
		{#1 \vspace{-2pt}}
	}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \hfill \small  #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubheadingTwo}[5]{
	\vspace{-1pt}\item{
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\textbf{\small #1} & \hfill  \small #2 \\
		\textit{\small#3} & \textit{\small #4} 
	\end{tabular*} \\ \vspace{1.5pt}
 \small #5 \vspace{-4pt}} 
}

\newcommand{\resumeSubheadingThree}[2]{
	\vspace{-1pt}\item{
		\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
			\textbf{\small #1} & \small #2 
		\end{tabular*} \vspace{-6pt}} 
}

\newcommand{\resumeSubheadingFour}[4]{
	\vspace{-1pt}\item{
		\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
			\textbf{\small #1}, \small #2, \small #3 & \small #4 
		\end{tabular*} \vspace{-6pt}} 
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Prem Shah}} & \small 4231 12th Ave NE Apt. No. 108, Seattle, WA - 98105\\ \small
  \href{https://www.linkedin.com/in/prem-shah-bb16aa10a/}{LinkedIn} $|$ \href{https://github.com/axelnine}{GitHub} & \small  Email : \href{mailto:prems2@uw.edu}{prems2@uw.edu} $|$ Mobile : +1-206-427-4930 \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheadingTwo
      {University of Washington, Information School}{Seattle, WA}
      {Master of Science in Information Management (Specialization in Data Science);  GPA: 3.8}{Sep. 2017 -- Jun. 2019}{Relevant Coursework: Theoretical Foundations of Data Science, Visualization Design, Analytical Methods for Research.}
      
    \resumeSubheadingTwo
      {Ahmedabad University, School of Engineering \& Applied Science}{ Ahmedabad, India}
      {Bachelor of Technology in Information \& Communication Technology}{Jul 2013 -- May 2017}{Relevant Coursework: Data Structures and Algorithms, Database Management Systems, Data Analytics \& Visualization, Linear  Algebra, Probability, Discrete Mathematics, Models of Computation, Internet of Things.}
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
\resumeSubHeadingListStart
\resumeSubItem{Languages}
{C, Python, R, SQL, HTML.}
\resumeSubItem{Libraries}
{Keras, Scikit-learn, Nltk, Pandas, Numpy, ggplot2, dplyr.}
\resumeSubItem{Tools}
{Tableau, Microsoft Excel, Weka, MATLAB, MySQL Workbench, Spyder.}

\resumeSubHeadingListEnd
\vspace{-9pt}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheadingTwo
      {Exponentia Datalabs}{Mumbai, India}{Intern, Data Analytics}{Jan 2017 -- Apr 2017}{\textit{Exponentia Datalabs is a growing analytics company specializing in end-to-end solutions for customer support analytics.}} \vspace{-2pt}
      \resumeItemListStart
		\resumeItemTwo{Migrated the sentiment analysis component of the company’s product from Support Vector Machines to Recurrent Neural Networks. Improved the accuracy of the model from 78\% to 86\%.}
		\resumeItemTwo{Researched and developed a phrase chunking component to extract noun, adjectives and verb phrases. Further improved the accuracy and precision by approximately 2\%. Integral component to extract multiple sentiments.} 
		\resumeItemTwo{Reduced training time by 10\% by optimizing different hyperparameters in keras.}
		\resumeItemTwo{Connected database through MySQL connector to give real-time sentiment analysis.}
		\resumeItemListEnd
    

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
  \resumeSubheadingThree
{Social Statistics: Studying opinions to understand migration}{\textit{Dec 2017 -- Current}}
\resumeItemListStart
\resumeItemTwo{Working as an independent researcher under Prof. Emilio Zagheni to understand migrant demography using LinkedIn \& Twitter data.}
\resumeItemTwo{Analyzing tweets from potential migrants to detect change in opinions and timing of migration.}
\resumeItemTwo{Understanding how migration affects socio-psychological factors like happiness.} 
\resumeItemListEnd

    \resumeSubheadingThree
{Quantitative Research: Factors affecting the ethical usage of assistive technology for dementia}{\textit{Sep 2017 -- Dec 2017}}
\resumeItemListStart
\resumeItemTwo{Used chi-square testing to check relation between various demographic variables and the level of impairment using the NACC dataset.}
\resumeItemTwo{Analyzed survey and telephonic interview data to understand trends regarding the knowledge of dementia.} 
\resumeItemTwo{Presented recommendations for improving the development of assistive technology conforming to our findings.}
\resumeItemListEnd

    \resumeSubheadingThree
{Data Modelling, Internet of Things: Intelligent Energy Consumption Module for Homes}{\textit{Aug 2016 -- Dec 2016}}
\resumeItemListStart
\resumeItemTwo{Applied weather data and household consumption dataset modelled on a Multivariate Linear Regression classifier from scratch to predict the power consumption of households to better organize power management. }
\resumeItemTwo{The system interfaced a temperature sensor to calculate indoor temperature, humidity and heat index.} 
\resumeItemTwo{Built and implemented algorithm to calculate highest consumption hours from data.}
\resumeItemListEnd

    \resumeSubheadingThree
{Database Management: Medical Search Engine}{\textit{Aug 2015 - Dec 2015}}
\resumeItemListStart
\resumeItemTwo{Integrated and developed user search for nearby medical facilities and information using MySQL. Included functionality to search for nearest hospitals and drugstores based on user’s current geographical location. }
\resumeItemTwo{Utilized user’s past search data and current geographical location to give results through querying and transaction processing. Also gave recommendations based on past searches.} 
\resumeItemTwo{Created wireframes for user interaction using Pencil. Awarded the Best Project in class.}
\resumeItemListEnd


\resumeSubHeadingListEnd

%
\section{Other Work Experience}
\resumeSubHeadingListStart
\resumeSubheadingFour
{University Of Washington Dining}{\textit{Student Assistant}}{Seattle, WA}{\textit{Sep 2017 -- Present}}\vspace{-1pt}
\resumeSubheadingFour
{Ahmedabad University}{\textit{Teaching Assistant (Computer Science 111)}}{Ahmedabad, India}{\textit{Jul 2016 -- Dec 2016}}\vspace{-1pt}
\resumeSubheadingFour
{Apang Manav Mandal (School for the Disabled)}{\textit{Teaching Volunteer}}{Ahmedabad, India}{\textit{Jul 2015 -- Sep 2015}}\vspace{-1pt}
\resumeSubHeadingListEnd
%-------------------------------------------
\end{document}